Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-03-29 paper/paper.tex
changed part of methodology to past tense

\documentclass[manuscript, screen]{acmart} %removing review removes the numbers on left side
% documentclass was [sigconf]{acmart} changed to match with the given overleaf link

@@

\renewcommand{\shortauthors}{Howlett, Spalding} %I don't know how to format this for three authors 
% the template does not show any shortauthors

@@

\subsection{Eye Tracking}
Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements. In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.

The EyeWriter 2.0 offers high-resolution tracking, capturing gaze patterns and fixations with accuracy. By analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.

Understanding the impact of music on cognitive response time and typing efficiency, as measured by the QBTest and eye tracking, can provide valuable insights for improving work and study environments where music is commonly used as a background stimulus.

\subsection{QBTest}
The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy. Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.

In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions. By administering the QBTest alongside eye tracking using EyeWriter 2.0, we aim to understand the impact of music on cognitive function and task performance.

The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks accurately. Through this research, we seek to provide insights that can enhance our understanding of how environmental factors, such as music, influence cognitive processes.

\subsection{Typing Test}
Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success. However, various factors can influence typing efficiency, including environmental stimuli such as music. Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.

This study uses a typing test to assess participants' typing performance under different music conditions. The test presents participants with lyrics from popular songs, simulating a real-world typing scenario where individuals may listen to music while working or studying.

By measuring typing speed and accuracy under conditions of music with lyrics, music without lyrics, and no music (silent condition), we aim to determine the impact of music on typing efficiency. This research will contribute to our understanding of how environmental factors, such as music, can affect cognitive processes related to typing and may have practical implications for improving productivity in various settings.

@@

\section{Methodology}
After obtaining consent from all participants, they will proceed to take the typing test. The test will present lyrics from popular songs within a graphical user interface (GUI). The interface will automatically calculate typing speed and accuracy in the program's backend, allowing participants to focus solely on completing the test. Each participant will complete the typing test under three conditions: Music with lyrics, Music without lyrics, and No music (silent condition).
Multiple levels of music intensity may be utilized within each condition to assess varying degrees of distraction.

Following the typing test, participants will proceed to the cognitive task component of the study, which will also be conducted under the three aforementioned conditions. % Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.

@@

\subsection[short]{Apparatus}
Apparatus
\subsubsection{EyeWriter 2.0}
\subsubsection{QB Test}
\subsubsection{Typing Test}

I will add typing methodology here.

>>>>

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% documentclass was [sigconf]{acmart} changed to match with the given overleaf link

@@

\renewcommand{\shortauthors}{Howlett, Spalding}
% the template does not show any shortauthors

@@

\subsection{Eye Tracking}
Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements. In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.
The EyeWriter 2.0 offers high-resolution tracking, capturing gaze patterns and fixations with accuracy. By analyzing participants' eye movements during the QBTest under different music conditions, we aim to understand how distractions, such as music, influence visual attention and cognitive performance.
Understanding the impact of music on cognitive response time and typing efficiency, as measured by the QBTest and eye tracking, can provide valuable insights for improving work and study environments where music is commonly used as a background stimulus.

\subsection{QBTest}
The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy. Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions. % This would be a good place to put a citation.
In this study, the QBTest serves as a central component for evaluating participants' cognitive response time and typing efficiency under various music conditions. By administering the QBTest alongside eye tracking using EyeWriter 2.0, we aim to understand the impact of music on cognitive function and task performance.
The QBTest's ability to quantify cognitive performance makes it an ideal tool for this study, allowing us to measure the effects of music on participants' ability to focus, process information, and perform tasks accurately. Through this research, we seek to provide insights that can enhance our understanding of how environmental factors, such as music, influence cognitive processes.

\subsection{Typing Test}
Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success. However, various factors can influence typing efficiency, including environmental stimuli such as music. Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.
This study uses a typing test to assess participants' typing performance under different music conditions. The test presents participants with lyrics from popular songs, simulating a real-world typing scenario where individuals may listen to music while working or studying.
By measuring typing speed and accuracy under conditions of music with lyrics, music without lyrics, and no music (silent condition), we aim to determine the impact of music on typing efficiency. This research will contribute to our understanding of how environmental factors, such as music, can affect cognitive processes related to typing and may have practical implications for improving productivity in various settings.

@@

\section{Methodology}
% After obtaining consent from all participants, they will proceed to take the typing test. The test will present lyrics from popular songs within a graphical user interface (GUI). 
After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
% The interface will automatically calculate typing speed and accuracy in the program's backend, allowing participants to focus solely on completing the test. Each participant will complete the typing test under three conditions: Music with lyrics, Music without lyrics, and No music (silent condition).
The interface automatically calculated typing speed and accuracy in the program's backend, allowing participants to focus soley on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
% Multiple levels of music intensity may be utilized within each condition to assess varying degrees of distraction.
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.

% Following the typing test, participants will proceed to the cognitive task component of the study, which will also be conducted under the three aforementioned conditions.
Following the typing test, participants proceeded to to the cognitive task component of the study, which were also conducted under the three aforementioned conditions. While the participants did the cognitive task of a quantified behavioral test, they wore the EyeWriter 2.0 glasses that we specially built for this study.
% Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.

@@

\subsection[short]{Apparatus}

\subsubsection{EyeWriter 2.0}
\subsubsection{QB Test}
\subsubsection{Typing Test}
The typing program was written in Python and compiled using Python3.9. While python can run on any device that has python installed, this study only used Macbook Pros running on Sonoma or MacOS 14. The singularity of the devices was used as the center of the screen for the typing test was hard coded when setting the starting position of the window for the typing test.
